Combining global tree cover loss data with national historical forest-cover maps to look at six decades of deforestation and forest fragmentation in Madagascar

### 2017-02-24 deforestmap.Rmd
Comparison with previous studies

We derived 30m cloud-free forest maps for Madagascar for the years 1990, 2000, 2010 and 2014 combining the 1990 and 2000 forest maps by @Harper2007 and the 2000-2014 tree percent cover map by @Hansen2013. On Harper's map, ~200,000 ha clouds are present over the ~4.2 million ha moist forest ecoregion (4.8% of clouds). To remove these clouds, we used the 2000 cloud-free tree percent cover map provided by @Hansen2013 (also at 30~m resolution) and we chose a threshold of 75% of tree cover [@Achard2014] to decide whether to replace cloud pixels with forest or non-forest pixels. We thus obtained a cloud-free year 2000 forest map for Madagascar. From this map, using tree cover loss data from 2000 to 2014 provided by @Hansen2013, we obtained cloud-free forest maps in 2010 and 2014 at 30~m resolution. Finally, we corrected the cloudy 1990 Harper forest map assuming that if forest was present in 2000, it was also present in 1990. Doing so, all clouds were removed and we obtained a cloud-free 1990 forest map for Madagascar. These maps are freely available at http:/bioscenemada.cirad.fr/forestmaps. On the basis of the forest-cover maps, we computed the mean annual deforestation intensity (in hectares of forest and in percentage) on six decades for 5 time periods from _c._ 1953 to 2014 (_c._ 1953-_c._ 1973-1990-2000-2010-2014).

@@

### 3.1 Validation

@@

### 3.2 Evolution of forest cover and deforestation intensity

@@

>>>>

We derived 30m cloud-free forest maps for Madagascar for the years 1990, 2000, 2010 and 2014 combining the 1990 and 2000 forest maps by @Harper2007 and the 2000-2014 tree cover and tree cover loss maps by @Hansen2013. On the 2000 Harper's map, ~200,000 ha clouds are present over the ~4.2 million ha moist forest ecoregion (4.8% of clouds). To remove these clouds, we used the 2000 cloud-free tree cover map provided by @Hansen2013 (also at 30~m resolution) and we chose a threshold of 75% of tree cover [@Achard2014] to decide whether to replace cloud pixels with forest or non-forest pixels. We thus obtained a cloud-free year 2000 forest map for Madagascar. From this map, using tree cover loss data from 2000 to 2014 provided by @Hansen2013, we obtained cloud-free forest maps in 2010 and 2014 at 30~m resolution. Finally, we corrected the cloudy 1990 Harper forest map assuming that if forest was present in 2000, it was also present in 1990. Doing so, all clouds were removed and we obtained a cloud-free 1990 forest map for Madagascar. 
For all forest cover maps, we also removed the isolated non-forest pixels if all the height surrounding pixels were covered by forest, assuming that small-scaled deforestation on a 30m square pixel inside the forest is unlikely. This was important in order not to over-estimate forest fragmentation.  
These maps are freely available at http:/bioscenemada.cirad.fr/forestmaps. On the basis of the forest-cover maps, we computed the mean annual deforestation intensity (in hectares of forest and in percentage) on six decades for 5 time periods from _c._ 1953 to 2014 (_c._ 1953-_c._ 1973-1990-2000-2010-2014).

@@

### 3.1 Evolution of forest cover and deforestation intensity

### 3.2 Comparison with previous forest-cover change studies in Madagascar

@@

@@

Should be used to actualize FAO report.

There has been a long debate about whether Madagascar has lost 90% of its forest since the arrival of the humans on the island [@Virah-Sawmy2009, @Agarwal2005]. What it sure now, is that Madgascar has lost around 50% of its natural forest in six decades since _c._ 1953.
